Transfer of Learned Opponent Models in Zero Sum Games

### 2020-01-29 Report/draft_report_v1.Rmd
report bug fixes

keywords          : "keywords"
wordcount         : "X"

@@

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r load-packages, include = FALSE}
library(papaja)
require(knitr)
require(citr)
require(bookdown)
# using some functions dplyr, ggpubr, PairedData and sjPlot. Need to be loaded. 
library(tidyr)
library(dplyr)
library(MASS)
library(ggpubr)
library(afex)
library(PairedData)
library(multcompView)
library(lsmeans)
```

@@

knitr::include_graphics("../Report/images/feedback_rps.png", dpi = 108)

>>>>

# keywords          : "keywords"
# wordcount         : "X"

@@

documentclass     : "apa6"
# classoption       : a4paper
classoption       : man
output            : papaja::apa6_pdf
---

```{r load-packages, include = FALSE}
library(papaja)
require(knitr)
require(citr)
require(bookdown)
# using some functions dplyr, ggpubr, PairedData and sjPlot. Need to be loaded. 
library(tidyr)
library(dplyr)
library(MASS)
library(ggpubr)
library(afex)
library(PairedData)
library(multcompView)
library(lsmeans)
library(magick)
```

@@

knitr::include_graphics("images/feedback_rps.png")

### 2020-01-29 Report/draft_report_v1.tex
report bug fixes

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Transfer of Learned Opponent Models in Zero Sum Games},
            pdfauthor={Ismail Guennouni~\& Maarten Speekenbrink},
            pdfkeywords={keywords},
            colorlinks=true,
            linkcolor=blue,
            filecolor=Maroon,
            citecolor=Blue,
            urlcolor=Blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the opponent strategy that may inform what actions they are likely to take next. Once we learn about the opponent's strategy, we can use this knowledge to inform how to best act in novel situations involving a previously encountered opponent. This may lead to very efficient generalization of knowledge, even to situations that are dissimilar to the history of interaction, assuming what we have learned about the opponent is an abstract representation that is not too dependent on the environment of the initial interaction. There is evidence that people learn models of the opponents when they play repeated economic games (Stahl \& Wilson, 1995), engage in bilateral negotiations (Baarslag, Hendrikx, Hindriks, \& Jonker, 2016), or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors (Weerd, Verbrugge, \& Verheij, 2012). In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations. These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities (Woodruff, Sciences, Brain, \& 1978, n.d.) play a role in determining human behaviour.

In order to explore learning transfer in strategic settings, it is generally useful to study simple games as a model of more complex interactions. More specifically, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards. Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are particularly adapted to the task of opponent modelling.

@@

{\centering \includegraphics{../Report/images/feedback_rps}

@@

{\centering \includegraphics{../Report/images/exp1_early_scor_game}

\caption{Average scores for rounds 2-6 by game in first experiment}\label{fig:exp1-early-score}
\end{figure}

In Figure~\ref{fig:exp1-early-score}, the average score across participants by game for rounds 2-6 are plotted. Scores are also averaged across levels of condition. We test the average scores for each game against a hypothesised value of 0 for a non-experienced player using parametric one sample t-tests. As expected for the initial RPS game, the average score is not significantly different from 0 as this is the first game and no learning is possible (t(148.85) = 1.04 , p = 0.89). In FWG, the score is significantly higher than 0 ( t(148.85) = 4.58 , p \textless{} 0.0001). This is also the case for the more dissimilar game : NUMBERS ( t(148.85) = 3.00, p = 0.0092).

@@

\caption{Avergae scores per game by opponcne type}\label{fig:exp2-score-by-opp}
\end{figure}

@@

To gain more insight into how participants played the games against the computer opponents, we compared multiple models of strategies the players may have been using to learn how to beat the opponent. As a base model, we assume play is random, and each potential action is chosen with equal probability. Note that this corresponds to the Nash equilibrium strategy.

Next, we include for comparison purposes a simple model-free reinforcement learning algorithm, that reinforces actions that have led to positive rewards, and conversely lowers the likelihood of choosing actions that led to a negative reward, irrespective of any state. We will use a simple temporal difference learning update rule:

@@

Where \(V_{t}(a)\) is the vlue associated with action \(a\) at time \(t\), \(\alpha\) is the learning rate and \(R_{t}\) the reward at time t. Actions are chosen based on action values using a softmax choice rule.

@@

In experiment 2, we allow this richer model to vary. In effect, we have a Q-learning model with a state space consisting of last round play, but in one instance, we fit a model (QLS) in which, when encountering an opponent, learning starts anew with no prior knowledge from previous encounters with the opponent used. In another instance, we fit a model in which what was learned about an opponent in the first interaction is transfered to the first round of the second interaction, so there is a within-game trasnfer of Q-values allowed (QLS-within). We fit both models to all participant's data in the second experiment where both opponents are faced.

@@

Next, we use a self-tuning Experience Weighted attraction model (Ho, Camerer, \& Chong, 2004). EWA models particularity is that thet nest two seemingly different approaches, namely reinforcement learning and belief learning. Belief based models are based on the assumption that players keep track of the frequency of past plays and best respond to that. In contrast, reinforcement learning does not take into account beliefs about other players, but is such that an action followed by a positive reward is more likely to be repeated than an action followed by a negative reward. The self-tuning EWA model has been shown to perform better than both these nested models in multiple repeated gmes and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.

Let's define some notation in order to write the pdate rule of the self-tuning EWA model. For player i, there are \(m_{i}\) strategies, denoted \(s_{i}^{j}\) (i.e player i's strategy number j). Strategies actually played by i in period t, are denoted \(s_{i}(t)\), while the opponent's strategy at time t is denoted \(s_{-i}(t)\). After playing \(s_{i}^{j}\) at time \(t\), player i payoff is denoted \(\pi_{i}(s_{i}^{j},s_{-i}(t))\), and the actual payoff the player received is \(\pi_{i}(t)\).

@@

Here, I(x,y) is the indicator function equla to 1 if \$ x = y\$ and 0 otherwise. A simple way to think about this update rule is that attractions are multipled by a parameter that represents experince (\(N(t-1)\)) which is itself decaying by a wight \(\phi\). The result is added to either the payoff received (when the indicator function is 0), or to \(\delta\) times the foregone payoff (when indicator function is 1). We can see that setting \(\delta = 0\) leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone payoffs, which is similar to weighted fictitous play (Cheung \& Friedman, 1994).
While the assumption in expanding the update rule above is that \(\phi\) and \(\delta\) are free parameters (Camerer, Ho, \& Others, 1997), the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in (Ho et al., 2004).

@@

In this set of models, we assume that participants have a belief that the opponent is a level-k agent, with uniform probability of the level k, and use evidence of past play to update their beliefs in a Bayesian way about the true value of k. We use values of k in \({0,1,2}\). We distinguish between multiple ToM models based on their ability to keep what was learned about the opponent in memory and hence facilitate transfer. In a No-Between-Transfer (NBT) model, players have no memory of what was learned about the opponent and start every new game assuming each level-k has equal probability. In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second intraction with the opponent, but are not able to transfer that learning to new games.

Conversely, In a Between-Transfer model (BT), players are assumed to keep in memory what was learned about the type of opponent faced (vector of probabilities of level-k) and use that at the beginning of each new game. In the context of experiment 2, we still assume that within game transfer is still present (from first to second interaction).

In experiment two, on top of these two models, we fit two other models: One in which we assume that players don't distinguish between the two opponents faced, so the opponent model vector is never updated (Naive). And finally, we also fit a model in which all stages of the game and all new games start with a fresh uniform probability of level-k opponent (NT), so no within or between opponent model learning transfer.

In summary, we fit two ToM models for experiment 1-play (NBT and BT), and 4 ToM models for experiment 2 ( NBT, BT, NT and Naive).In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood. Using information criteria based Bayesian model comparison (BIC), the best fitting model for each participant was chosen and we compared the number of participants whose behavior was best explained by each model.

@@

Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure~\ref{fig:exp2-cumScores}, in that participants whose behavior was best fit by a ToM model of learning the oppponent strategy had the highest cumulative performance, followed by theose relying on reinforcement learning with a state space of last round play, and as expected random play as well as EWA were at the bottom of cumulative performance.

@@

\leavevmode\hypertarget{ref-Cooper2008}{}%
Cooper, D. J., \& Kagel, J. H. (2008). Learning and transfer in signaling games. \emph{Economic Theory}, \emph{34}(3), 415--439. \url{https://doi.org/10.1007/s00199-006-0192-5}

@@

\leavevmode\hypertarget{ref-Haruvy2012}{}%
Haruvy, E., \& Stahl, D. O. (2012). Between-game rule learning in dissimilar symmetric normal-form games. \emph{Games and Economic Behavior}, \emph{74}(1), 208--221. \url{https://doi.org/10.1016/j.geb.2011.06.001}

\leavevmode\hypertarget{ref-ho2004economics}{}%
Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). \emph{The economics of learning models: A self-tuning theory of learning in games}.

@@

\leavevmode\hypertarget{ref-Juvina2013}{}%
Juvina, I., Saleem, M., Martin, J. M., Gonzalez, C., \& Lebiere, C. (2013). Reciprocal trust mediates deep transfer of learning between games of strategic interaction. \emph{Organizational Behavior and Human Decision Processes}, \emph{120}(2), 206--215. \url{https://doi.org/10.1016/j.obhdp.2012.09.004}

@@

\leavevmode\hypertarget{ref-Lake2017}{}%
Lake, B. M., Ullman, T. D., Tenenbaum, J. B., \& Gershman, S. J. (2017). Building machines that learn and think like people. \emph{Behavioral and Brain Sciences}, \emph{40}. \url{https://doi.org/10.1017/S0140525X16001837}

@@

\leavevmode\hypertarget{ref-de2012higher}{}%
Weerd, H. de, Verbrugge, R., \& Verheij, B. (2012). Higher-order social cognition in rock-paper-scissors: A simulation study. \emph{Proceedings of the 11th international conference on autonomous agents and multiagent systems-volume 3}, 1195--1196.

\leavevmode\hypertarget{ref-Woodruff}{}%
Woodruff, G., Sciences, D. P. B., Brain, \& 1978. (n.d.). \emph{Does the chimpanzee have a theory of mind}.

>>>>

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Transfer of Learned Opponent Models in Zero Sum Games},
            pdfauthor={Ismail Guennouni~\& Maarten Speekenbrink},
            colorlinks=true,
            linkcolor=blue,
            filecolor=Maroon,
            citecolor=Blue,
            urlcolor=Blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the person we are interacting with that may inform what actions they are likely to take next. Once we learn something about them, we can use this knowledge to inform how to best behave in novel situations. This may lead to very efficient generalization of knowledge, even to situations that are dissimilar to the history of interaction, assuming what we have learned about others is an abstract representation that is not too dependent on the environment of the initial interaction. There is evidence that people learn models of their opponents when they play repeated economic games (Stahl \& Wilson, 1995), engage in bilateral negotiations (Baarslag, Hendrikx, Hindriks, \& Jonker, 2016), or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors (Weerd, Verbrugge, \& Verheij, 2012). In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations. These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities (Woodruff, Sciences, Brain, \& 1978, n.d.) play a role in determining human behaviour. In order to explore learning transfer in these strategic settings, it is generally useful to study simple games as a model of more complex interactions. More specifically, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards. Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are particularly adapted to the task of opponent modelling.

@@

{\centering \includegraphics{images/feedback_rps}

@@

We test the average scores for each game against a hypothesised value of 0 for a non-experienced player using parametric one sample t-tests. As expected for the initial RPS game, the average score is not significantly different from 0 as this is the first game and no learning is possible (t(148.85) = 1.04 , p = 0.89). In FWG, the score is significantly higher than 0 ( t(148.85) = 4.58 , p \textless{} 0.0001). This is also the case for the more dissimilar game : NUMBERS ( t(148.85) = 3.00, p = 0.0092).

@@

\caption{Average scores per game by opponent type}\label{fig:exp2-score-by-opp}
\end{figure}

@@

To gain more insight into how participants played the games against the computer opponents, we compared multiple models of strategies the players may have been using to learn how to beat the opponent. As a base model, we assume play is random, and each potential action is chosen with equal probability. Note that this corresponds to the Nash equilibrium strategy. In this sectionn, we will go through the various models we have used and explain how they update what they learn about the game or the opponent

\hypertarget{reinforcement-learning}{%
\subsection{Reinforcement Learning}\label{reinforcement-learning}}

We include for comparison purposes a simple model-free reinforcement learning algorithm, that reinforces actions that have led to positive rewards, and conversely lowers the likelihood of choosing actions that led to a negative reward, irrespective of any state. We will use a simple temporal difference learning update rule:

@@

Where \(V_{t}(a)\) is the value associated with action \(a\) at time \(t\), \(\alpha\) is the learning rate and \(R_{t}\) the reward at time t. Actions are chosen based on action values using a softmax choice rule.

@@

In experiment 2, we allow this richer model to have a memory of the interaction. In effect, we have a Q-learning model with a state space consisting of last round play, but in one instance, we fit a model (QLS) in which, when encountering an opponent, learning starts anew with no prior knowledge from previous encounters with the opponent used. In another instance, we fit a model in which what was learned about an opponent in the first interaction is transfered to the first round of the second interaction, so there is a within-game trasnfer of Q-values allowed (QLS-within). We fit both models to all participant's data in the second experiment where both opponents are faced.

@@

Next, we use a self-tuning Experience Weighted attraction model (Ho, Camerer, \& Chong, 2004). EWA models particularity is that thet nest two seemingly different approaches, namely reinforcement learning and belief learning. Belief based models are based on the assumption that players keep track of the frequency of past plays and best respond to that. In contrast, reinforcement learning does not take into account beliefs about other players, but is such that an action followed by a positive reward is more likely to be repeated than an action followed by a negative reward. The self-tuning EWA model has been shown to perform better than both these nested models in multiple repeated games and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.

Let's define some notation in order to write the update rule of the self-tuning EWA model. For player i, there are \(m_{i}\) strategies, denoted \(s_{i}^{j}\) (i.e player i's strategy number j). Strategies actually played by i in period t, are denoted \(s_{i}(t)\), while the opponent's strategy at time t is denoted \(s_{-i}(t)\). After playing \(s_{i}^{j}\) at time \(t\), player i payoff is denoted \(\pi_{i}(s_{i}^{j},s_{-i}(t))\), and the actual payoff the player received is \(\pi_{i}(t)\).

@@

Here, I(x,y) is the indicator function equal to 1 if \$ x = y\$ and 0 otherwise. A simple way to think about this update rule is that attractions are multipled by a parameter that represents experince (\(N(t-1)\)) which is itself decaying by a wight \(\phi\). The result is added to either the payoff received (when the indicator function is 0), or to \(\delta\) times the foregone payoff (when indicator function is 1). We can see that setting \(\delta = 0\) leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone payoffs, which is similar to weighted fictitous play (Cheung \& Friedman, 1994).
While the assumption in expanding the update rule above is that \(\phi\) and \(\delta\) are free parameters (Camerer, Ho, \& Others, 1997), the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in (Ho et al., 2004).

@@

In this set of models, we assume that participants have a belief that the opponent is a level-k agent, with uniform probability of the level k, and use evidence of past play to update their beliefs in a Bayesian way about the true value of k. We use values of k in \({0,1,2}\). We distinguish between multiple ToM models based on their ability to keep what was learned about the opponent in memory and hence facilitate transfer. In a No-Between-Transfer (NBT) model, players have no memory of what was learned about the opponent and start every new game assuming each level-k has equal probability. In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second interaction with the opponent, but are not able to transfer that learning to new games (So within but no between trasnfer)

Conversely, In a Between-Transfer model (BT), players are assumed to keep in memory what was learned about the type of opponent faced (vector of probabilities of level-k) and use that at the beginning of each new game. In the context of experiment 2, we still assume that if between transfer is present, then within game transfer is also present (from first to second interaction).

We fit the above two models to experiment 1 data. In experiment two, on top of these two models, we fit two other models: One in which we assume that players don't distinguish between the two opponents faced, so the opponent model vector is never updated (Naive). And finally, we also fit a model in which all stages of the game and all new games start with a fresh uniform probability of level-k opponent (NT), so no within or between opponent model learning transfer.

In summary, we fit two ToM models for experiment 1-play (NBT and BT), and 4 ToM models for experiment 2 ( NBT, BT, NT and Naive). In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood. Using information criteria based Bayesian model comparison (BIC), the best fitting model for each participant was chosen and we compared the number of participants whose behavior was best explained by each model.

@@

Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure~\ref{fig:exp2-cumScores}, in that participants whose behavior was best fit by a ToM model of learning the oppponent strategy had the highest cumulative performance. Out of these ToM models, the one in which there is within-game but no between-game transfer (NBT) had the best cumulative performance, folowed by a model in which both within and between trasnfer of opponent models is allowed (BT). The next best model from a performance perspective was a Q-learning model with states and within game transfer, followed by ToM models where either players started learning from scratch at each stage of each game (NT) and the model in which they didn't distinguish between opponenets (Naive). As expected, random play as well as self-tuning EWA were at the bottom of cumulative performance.

@@

\leavevmode\hypertarget{ref-Cooper2008}{}%
Cooper, D. J., \& Kagel, J. H. (2008). Learning and transfer in signaling games. \emph{Economic Theory}, \emph{34}(3), 415--439. doi:\href{https://doi.org/10.1007/s00199-006-0192-5}{10.1007/s00199-006-0192-5}

@@

\leavevmode\hypertarget{ref-Haruvy2012}{}%
Haruvy, E., \& Stahl, D. O. (2012). Between-game rule learning in dissimilar symmetric normal-form games. \emph{Games and Economic Behavior}, \emph{74}(1), 208--221. doi:\href{https://doi.org/10.1016/j.geb.2011.06.001}{10.1016/j.geb.2011.06.001}

\leavevmode\hypertarget{ref-ho2004economics}{}%
Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). The economics of learning models: A self-tuning theory of learning in games.

@@

\leavevmode\hypertarget{ref-Juvina2013}{}%
Juvina, I., Saleem, M., Martin, J. M., Gonzalez, C., \& Lebiere, C. (2013). Reciprocal trust mediates deep transfer of learning between games of strategic interaction. \emph{Organizational Behavior and Human Decision Processes}, \emph{120}(2), 206--215. doi:\href{https://doi.org/10.1016/j.obhdp.2012.09.004}{10.1016/j.obhdp.2012.09.004}

@@

\leavevmode\hypertarget{ref-Lake2017}{}%
Lake, B. M., Ullman, T. D., Tenenbaum, J. B., \& Gershman, S. J. (2017). Building machines that learn and think like people. \emph{Behavioral and Brain Sciences}, \emph{40}. doi:\href{https://doi.org/10.1017/S0140525X16001837}{10.1017/S0140525X16001837}

@@

\leavevmode\hypertarget{ref-de2012higher}{}%
Weerd, H. de, Verbrugge, R., \& Verheij, B. (2012). Higher-order social cognition in rock-paper-scissors: A simulation study. In \emph{Proceedings of the 11th international conference on autonomous agents and multiagent systems-volume 3} (pp. 1195--1196).

\leavevmode\hypertarget{ref-Woodruff}{}%
Woodruff, G., Sciences, D. P. B., Brain, \& 1978. (n.d.). Does the chimpanzee have a theory of mind.
